Blocking-resistant communication\\through domain fronting

### 2014-07-25 docs/meek.tex
Protocol sample.
Cribbed from
https://trac.torproject.org/projects/tor/wiki/doc/AChildsGardenOfPluggableTransports#meek.

The main technical challenge is handling a TCP stream
that has been split up into a sequence of HTTP requests and responses.
The body of each HTTP request and HTTP response carries
a small chunk of upstream or downstream communication.
\meekserver\ must handle many clients at once,
and therefore maintains many open connections to the local Tor process,
one for each active client.
When a new request arrives, the server must determine which
open session it belongs to
(or whether it is a brand-new client needing a new session).
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but that doesn't work for meek for two reasons:
the source IP of the requests is that of the intermediate web service,
not that of the client;
and a logical stream is chopped into multiple independent HTTP requests,
so the source port is always changing.
Rather, each client generates a random 256-bit session ID,
which it sends with each of its requests in a special
X-Session-ID header.
\meekserver, when it sees a session ID for the first time,
opens up a new connection to the local Tor process
and associates the connection and ID in a cache.
Subsequent requests with the
same session ID will reuse the same Tor connection.
Sessions are closed after a period of inactivity.
Figure~\ref{fig:protocol} shows an sample of the protocol.

\begin{figure}
% Use a child's garden--like figure of the HTTP protocol here.
\caption{
The meek protocol.
The session ID is randomly generated by the client.
The protocol shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor is unable to classify the traffic based on the
Host or X-Session-ID headers.
}
\label{fig:protocol}
\end{figure}

>>>>

The main technical challenge is handling a TCP stream
that has been split up into a sequence of HTTP requests and responses.
The body of each HTTP request and HTTP response carries
a small chunk of upstream or downstream communication.
\meekserver\ must handle many clients at once,
and therefore maintains many open connections to the local Tor process,
one for each active client.
When a new request arrives, the server must determine which
open session it belongs to
(or whether it is a brand-new client needing a new session).
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but that doesn't work for meek for two reasons:
the source IP of the requests is that of the intermediate web service,
not that of the client;
and a logical stream is chopped into multiple independent HTTP requests,
so the source port is always changing.
Rather, each client generates a random 256-bit session ID,
which it sends with each of its requests in a special
X-Session-ID header.
\meekserver, when it sees a session ID for the first time,
opens up a new connection to the local Tor process
and associates the connection and ID in a cache.
Subsequent requests with the
same session ID will reuse the same Tor connection.
Sessions are closed after a period of inactivity.
Figure~\ref{fig:protocol} shows a sample of the protocol.

\begin{figure}
% Use a child's garden--like figure of the HTTP protocol here.
\tiny
\usefont{U}{cmtt}{m}{n}%
\begin{verbatim}
POST / HTTP/1.1
Host: forbidden.example
X-Session-Id: cbIzfhx1Hn+RHURmIPhjgY+W3B6zA8Ua6dd92DLscOE=
Content-Length: 517

\x16\x03\x01\x02\x00\x01\x00\x01\xfc\x03\x03\x9b\xa9\x9f\xf5\xbb
...
\end{verbatim}
\begin{quote}
\begin{verbatim}
HTTP/1.1 200 OK
Content-Length: 739

\x16\x03\x03\x00\x3e\x02\x00\x00\x3a\x03\x03\x53\x75\xa2\x78\x7d
...
\end{verbatim}
\end{quote}
\begin{verbatim}
POST / HTTP/1.1
Host: forbidden.example
X-Session-Id: cbIzfhx1Hn+RHURmIPhjgY+W3B6zA8Ua6dd92DLscOE=
Content-Length: 0

\end{verbatim}
\begin{quote}
\begin{verbatim}
HTTP/1.1 200 OK
Content-Length: 75\r\n

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25\x72\x1e
...
\end{verbatim}
\end{quote}
\caption{
The meek protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02...}
is the beginning of a TLS handshake).
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and X-Session-ID headers for classification.
}
\label{fig:protocol}
\end{figure}
